---
title: 'Multiple Groups BCH and Vermunt: Preliminary Results'
author: "Veronica Cole"
date: "Monday, May 07, 2018"
output: html_document
---

After obtaining suspect results in validity analyses using Vermunt and BCH adjustments for uncertainty, we have rerun the analyses using a different parameterization. Specifically, rather than using a MIMIC model in which study membership affects the probability of AUD (i.e., impact) as well as item endorsement probabilities (i.e., DIF), we now parameterize the model as a four-class multiple groups model in which class membership captures both study (with classes 1 and 2 representing Study 1, and classes 3 and 4 representing Study 2) and AUD diagnosis (with classes 1 and 3 representing diagnosed cases, and classes 2 and 4 representing undiagnosed cases). The benefits of this parameterization are that we can use the matrix of misclassification probabilities provided by Mplus both to calculate misclassification logits (for Vermunt) and probability weights (for BCH). 

We have some preliminary results. First, we examine the case in which there is neither impact nor DIF in the data generating model, and in which only impact is present in the fitted model, to determine whether results are believable before getting to the question of whether DIF and impact affect the accuracy of estimates. 

```{r,echo=FALSE,message=FALSE,warning=FALSE,echo=FALSE,cache=TRUE}
c1l0<-c("i0d0c1l0n25","i0d1c1l0n25","i1d0c1l0n25","i1d1c1l0n25","i0d0c1l0n50","i0d1c1l0n50","i1d0c1l0n50","i1d1c1l0n50","i0d0c1l0n100","i0d1c1l0n100","i1d0c1l0n100","i1d1c1l0n100")
c1l1<-c("i0d0c1l1n25","i0d1c1l1n25","i1d0c1l1n25","i1d1c1l1n25","i0d0c1l1n50","i0d1c1l1n50","i1d0c1l1n50","i1d1c1l1n50","i0d0c1l1n100","i0d1c1l1n100","i1d0c1l1n100","i1d1c1l1n100")
c2l0<-c("i0d0c2l0n25","i0d1c2l0n25","i1d0c2l0n25","i1d1c2l0n25","i0d0c2l0n50","i0d1c2l0n50","i1d0c2l0n50","i1d1c2l0n50","i0d0c2l0n100","i0d1c2l0n100","i1d0c2l0n100","i1d1c2l0n100")
c2l1<-c("i0d0c2l1n25","i0d1c2l1n25","i1d0c2l1n25","i1d1c2l1n25","i0d0c2l1n50","i0d1c2l1n50","i1d0c2l1n50","i1d1c2l1n50","i0d0c2l1n100","i0d1c2l1n100","i1d0c2l1n100","i1d1c2l1n100")
all.sets<-list(c1l0,c1l1,c2l0,c2l1)

names.c1l0<-c('ACY2','ACY3','ACY4','ACY6','ACY12','ACY14')
names.c1l1<-c('ACY1','ACY2','ACY3','ACY4','ACY5','ACY6','ACY7','ACY8','ACY9','ACY10','ACY12','ACY13','ACY14','ACY15','ACY18')
names.c2l0<-c('AMT10','AMT11','AMT12','AMT14','AMT16','AMT18')
names.c2l1<-c('AMT8','AMT9','AMT10','AMT11','AMT12','AMT13','AMT14','AMT15','AMT16','AMT17','AMT18')

all.names<-list(names.c1l0,names.c1l1,names.c2l0,names.c2l1)
full.names<-list(names.c1l1,names.c1l1,names.c2l1,names.c2l1)


library(MplusAutomation)



# Intercept-only models ---------------------------------------------------
c1.test.v.io.frat<-array(NA,dim=c(100,12,4))
c3.test.v.io.frat<-array(NA,dim=c(100,12,4))
c1.test.bch.io.frat<-array(NA,dim=c(100,12,4))
c3.test.bch.io.frat<-array(NA,dim=c(100,12,4))
c1.test.v.io.gender<-array(NA,dim=c(100,12,4))
c3.test.v.io.gender<-array(NA,dim=c(100,12,4))
c1.test.bch.io.gender<-array(NA,dim=c(100,12,4))
c3.test.bch.io.gender<-array(NA,dim=c(100,12,4))

for (i in 1:4){
  for (j in 1:12) {
    for (r in 1:100) {
      the.output.v.io.frat<-readModels(paste0("M:/xstudy2/Simulation/aim02/July2017/sim/knownclass/rerun/",all.sets[[i]][j],"/",all.sets[[i]][j],"_io_r",r,"_v_frat.out"))$parameters
      the.output.bch.io.frat<-readModels(paste0("M:/xstudy2/Simulation/aim02/July2017/sim/knownclass/rerun/",all.sets[[i]][j],"/",all.sets[[i]][j],"_io_r",r,"_bch_frat.out"))$parameters
      the.output.v.io.gender<-readModels(paste0("M:/xstudy2/Simulation/aim02/July2017/sim/knownclass/rerun/",all.sets[[i]][j],"/",all.sets[[i]][j],"_io_r",r,"_v_gender.out"))$parameters
      the.output.bch.io.gender<-readModels(paste0("M:/xstudy2/Simulation/aim02/July2017/sim/knownclass/rerun/",all.sets[[i]][j],"/",all.sets[[i]][j],"_io_r",r,"_bch_gender.out"))$parameters
      if (length(the.output.v.io.frat)>0) {
        c1.4.v.io.frat<-subset(the.output.v.io.frat$unstandardized$est,the.output.v.io.frat$unstandardized$paramHeader=="C#1.ON")
        c2.4.v.io.frat<-subset(the.output.v.io.frat$unstandardized$est,the.output.v.io.frat$unstandardized$paramHeader=="C#2.ON")
        c3.4.v.io.frat<-subset(the.output.v.io.frat$unstandardized$est,the.output.v.io.frat$unstandardized$paramHeader=="C#3.ON")
        c1.test.v.io.frat[r,j,i]<-c1.4.v.io.frat-c2.4.v.io.frat
        c3.test.v.io.frat[r,j,i]<-c3.4.v.io.frat
      }
      if (length(the.output.bch.io.frat)>0) {
        c1.4.bch.io.frat<-subset(the.output.bch.io.frat$unstandardized$est,the.output.bch.io.frat$unstandardized$paramHeader=="C#1.ON")
        c2.4.bch.io.frat<-subset(the.output.bch.io.frat$unstandardized$est,the.output.bch.io.frat$unstandardized$paramHeader=="C#2.ON")
        c3.4.bch.io.frat<-subset(the.output.bch.io.frat$unstandardized$est,the.output.bch.io.frat$unstandardized$paramHeader=="C#3.ON")
        c1.test.bch.io.frat[r,j,i]<-c1.4.bch.io.frat-c2.4.bch.io.frat
        c3.test.bch.io.frat[r,j,i]<-c3.4.bch.io.frat
      }
      if (length(the.output.v.io.gender)>0) {
        c1.4.v.io.gender<-subset(the.output.v.io.gender$unstandardized$est,the.output.v.io.gender$unstandardized$paramHeader=="C#1.ON")
        c2.4.v.io.gender<-subset(the.output.v.io.gender$unstandardized$est,the.output.v.io.gender$unstandardized$paramHeader=="C#2.ON")
        c3.4.v.io.gender<-subset(the.output.v.io.gender$unstandardized$est,the.output.v.io.gender$unstandardized$paramHeader=="C#3.ON")
        c1.test.v.io.gender[r,j,i]<-c1.4.v.io.gender-c2.4.v.io.gender
        c3.test.v.io.gender[r,j,i]<-c3.4.v.io.gender
      }
      if (length(the.output.bch.io.gender)>0) {
        c1.4.bch.io.gender<-subset(the.output.bch.io.gender$unstandardized$est,the.output.bch.io.gender$unstandardized$paramHeader=="C#1.ON")
        c2.4.bch.io.gender<-subset(the.output.bch.io.gender$unstandardized$est,the.output.bch.io.gender$unstandardized$paramHeader=="C#2.ON")
        c3.4.bch.io.gender<-subset(the.output.bch.io.gender$unstandardized$est,the.output.bch.io.gender$unstandardized$paramHeader=="C#3.ON")
        c1.test.bch.io.gender[r,j,i]<-c1.4.bch.io.gender-c2.4.bch.io.gender
        c3.test.bch.io.gender[r,j,i]<-c3.4.bch.io.gender
      }
    }
  }
}


c1l0<-c("i0d0c1l0n25","i0d1c1l0n25","i1d0c1l0n25","i1d1c1l0n25","i0d0c1l0n50","i0d1c1l0n50","i1d0c1l0n50","i1d1c1l0n50","i0d0c1l0n100","i0d1c1l0n100","i1d0c1l0n100","i1d1c1l0n100")
c1l1<-c("i0d0c1l1n25","i0d1c1l1n25","i1d0c1l1n25","i1d1c1l1n25","i0d0c1l1n50","i0d1c1l1n50","i1d0c1l1n50","i1d1c1l1n50","i0d0c1l1n100","i0d1c1l1n100","i1d0c1l1n100","i1d1c1l1n100")
c2l0<-c("i0d0c2l0n25","i0d1c2l0n25","i1d0c2l0n25","i1d1c2l0n25","i0d0c2l0n50","i0d1c2l0n50","i1d0c2l0n50","i1d1c2l0n50","i0d0c2l0n100","i0d1c2l0n100","i1d0c2l0n100","i1d1c2l0n100")
c2l1<-c("i0d0c2l1n25","i0d1c2l1n25","i1d0c2l1n25","i1d1c2l1n25","i0d0c2l1n50","i0d1c2l1n50","i1d0c2l1n50","i1d1c2l1n50","i0d0c2l1n100","i0d1c2l1n100","i1d0c2l1n100","i1d1c2l1n100")
all.sets<-list(c1l0,c1l1,c2l0,c2l1)

title.list<-c("Consequences, Long","Consequences, Short"," Motives, Long","Motives, Short")

trimmed.bch.io.frat<-c3.test.bch.io.frat
trimmed.bch.io.gender<-c3.test.bch.io.gender
trimmed.v.io.frat<-c3.test.v.io.frat
trimmed.v.io.gender<-c3.test.v.io.gender

for (a in 1:100) {
  for (b in 1:12) {
    for (d in 1:4) {
      if ((is.na(c3.test.bch.io.frat[a,b,d])==FALSE)&(abs(c3.test.bch.io.frat[a,b,d])>10))
      {trimmed.bch.io.frat[a,b,d]<-NA}
      if ((is.na(c3.test.bch.io.gender[a,b,d])==FALSE)&(abs(c3.test.bch.io.gender[a,b,d])>10))
      {trimmed.bch.io.gender[a,b,d]<-NA}
      if ((is.na(c3.test.v.io.frat[a,b,d])==FALSE)&(abs(c3.test.v.io.frat[a,b,d])>10))
      {trimmed.v.io.frat[a,b,d]<-NA}
      if ((is.na(c3.test.v.io.gender[a,b,d])==FALSE)&(abs(c3.test.v.io.gender[a,b,d])>10))
      {trimmed.v.io.gender[a,b,d]<-NA}
    }
  }
}


# Uniform DIF models ---------------------------------------------------
c1.test.v.ud.frat<-array(NA,dim=c(100,12,4))
c3.test.v.ud.frat<-array(NA,dim=c(100,12,4))
c1.test.bch.ud.frat<-array(NA,dim=c(100,12,4))
c3.test.bch.ud.frat<-array(NA,dim=c(100,12,4))
c1.test.v.ud.gender<-array(NA,dim=c(100,12,4))
c3.test.v.ud.gender<-array(NA,dim=c(100,12,4))
c1.test.bch.ud.gender<-array(NA,dim=c(100,12,4))
c3.test.bch.ud.gender<-array(NA,dim=c(100,12,4))

for (i in 1:4){
  for (j in 1:12) {
    for (r in 1:100) {
      the.output.v.ud.frat<-readModels(paste0("M:/xstudy2/Simulation/aim02/July2017/sim/knownclass/rerun/",all.sets[[i]][j],"/",all.sets[[i]][j],"_ud_r",r,"_v_frat.out"))$parameters
      the.output.bch.ud.frat<-readModels(paste0("M:/xstudy2/Simulation/aim02/July2017/sim/knownclass/rerun/",all.sets[[i]][j],"/",all.sets[[i]][j],"_ud_r",r,"_bch_frat.out"))$parameters
      the.output.v.ud.gender<-readModels(paste0("M:/xstudy2/Simulation/aim02/July2017/sim/knownclass/rerun/",all.sets[[i]][j],"/",all.sets[[i]][j],"_ud_r",r,"_v_gender.out"))$parameters
      the.output.bch.ud.gender<-readModels(paste0("M:/xstudy2/Simulation/aim02/July2017/sim/knownclass/rerun/",all.sets[[i]][j],"/",all.sets[[i]][j],"_ud_r",r,"_bch_gender.out"))$parameters
      if (length(the.output.v.ud.frat)>0) {
        c1.4.v.ud.frat<-subset(the.output.v.ud.frat$unstandardized$est,the.output.v.ud.frat$unstandardized$paramHeader=="C#1.ON")
        c2.4.v.ud.frat<-subset(the.output.v.ud.frat$unstandardized$est,the.output.v.ud.frat$unstandardized$paramHeader=="C#2.ON")
        c3.4.v.ud.frat<-subset(the.output.v.ud.frat$unstandardized$est,the.output.v.ud.frat$unstandardized$paramHeader=="C#3.ON")
        c1.test.v.ud.frat[r,j,i]<-c1.4.v.ud.frat-c2.4.v.ud.frat
        c3.test.v.ud.frat[r,j,i]<-c3.4.v.ud.frat
      }
      if (length(the.output.bch.ud.frat)>0) {
        c1.4.bch.ud.frat<-subset(the.output.bch.ud.frat$unstandardized$est,the.output.bch.ud.frat$unstandardized$paramHeader=="C#1.ON")
        c2.4.bch.ud.frat<-subset(the.output.bch.ud.frat$unstandardized$est,the.output.bch.ud.frat$unstandardized$paramHeader=="C#2.ON")
        c3.4.bch.ud.frat<-subset(the.output.bch.ud.frat$unstandardized$est,the.output.bch.ud.frat$unstandardized$paramHeader=="C#3.ON")
        c1.test.bch.ud.frat[r,j,i]<-c1.4.bch.ud.frat-c2.4.bch.ud.frat
        c3.test.bch.ud.frat[r,j,i]<-c3.4.bch.ud.frat
      }
      if (length(the.output.v.ud.gender)>0) {
        c1.4.v.ud.gender<-subset(the.output.v.ud.gender$unstandardized$est,the.output.v.ud.gender$unstandardized$paramHeader=="C#1.ON")
        c2.4.v.ud.gender<-subset(the.output.v.ud.gender$unstandardized$est,the.output.v.ud.gender$unstandardized$paramHeader=="C#2.ON")
        c3.4.v.ud.gender<-subset(the.output.v.ud.gender$unstandardized$est,the.output.v.ud.gender$unstandardized$paramHeader=="C#3.ON")
        c1.test.v.ud.gender[r,j,i]<-c1.4.v.ud.gender-c2.4.v.ud.gender
        c3.test.v.ud.gender[r,j,i]<-c3.4.v.ud.gender
      }
      if (length(the.output.bch.ud.gender)>0) {
        c1.4.bch.ud.gender<-subset(the.output.bch.ud.gender$unstandardized$est,the.output.bch.ud.gender$unstandardized$paramHeader=="C#1.ON")
        c2.4.bch.ud.gender<-subset(the.output.bch.ud.gender$unstandardized$est,the.output.bch.ud.gender$unstandardized$paramHeader=="C#2.ON")
        c3.4.bch.ud.gender<-subset(the.output.bch.ud.gender$unstandardized$est,the.output.bch.ud.gender$unstandardized$paramHeader=="C#3.ON")
        c1.test.bch.ud.gender[r,j,i]<-c1.4.bch.ud.gender-c2.4.bch.ud.gender
        c3.test.bch.ud.gender[r,j,i]<-c3.4.bch.ud.gender
      }
    }
  }
}


c1l0<-c("i0d0c1l0n25","i0d1c1l0n25","i1d0c1l0n25","i1d1c1l0n25","i0d0c1l0n50","i0d1c1l0n50","i1d0c1l0n50","i1d1c1l0n50","i0d0c1l0n100","i0d1c1l0n100","i1d0c1l0n100","i1d1c1l0n100")
c1l1<-c("i0d0c1l1n25","i0d1c1l1n25","i1d0c1l1n25","i1d1c1l1n25","i0d0c1l1n50","i0d1c1l1n50","i1d0c1l1n50","i1d1c1l1n50","i0d0c1l1n100","i0d1c1l1n100","i1d0c1l1n100","i1d1c1l1n100")
c2l0<-c("i0d0c2l0n25","i0d1c2l0n25","i1d0c2l0n25","i1d1c2l0n25","i0d0c2l0n50","i0d1c2l0n50","i1d0c2l0n50","i1d1c2l0n50","i0d0c2l0n100","i0d1c2l0n100","i1d0c2l0n100","i1d1c2l0n100")
c2l1<-c("i0d0c2l1n25","i0d1c2l1n25","i1d0c2l1n25","i1d1c2l1n25","i0d0c2l1n50","i0d1c2l1n50","i1d0c2l1n50","i1d1c2l1n50","i0d0c2l1n100","i0d1c2l1n100","i1d0c2l1n100","i1d1c2l1n100")
all.sets<-list(c1l0,c1l1,c2l0,c2l1)

title.list<-c("Consequences, Long","Consequences, Short"," Motives, Long","Motives, Short")

trimmed.bch.ud.frat<-c3.test.bch.ud.frat
trimmed.bch.ud.gender<-c3.test.bch.ud.gender
trimmed.v.ud.frat<-c3.test.v.ud.frat
trimmed.v.ud.gender<-c3.test.v.ud.gender

for (a in 1:100) {
  for (b in 1:12) {
    for (d in 1:4) {
      if ((is.na(c3.test.bch.ud.frat[a,b,d])==FALSE)&(abs(c3.test.bch.ud.frat[a,b,d])>10))
      {trimmed.bch.ud.frat[a,b,d]<-NA}
      if ((is.na(c3.test.bch.ud.gender[a,b,d])==FALSE)&(abs(c3.test.bch.ud.gender[a,b,d])>10))
      {trimmed.bch.ud.gender[a,b,d]<-NA}
      if ((is.na(c3.test.v.ud.frat[a,b,d])==FALSE)&(abs(c3.test.v.ud.frat[a,b,d])>10))
      {trimmed.v.ud.frat[a,b,d]<-NA}
      if ((is.na(c3.test.v.ud.gender[a,b,d])==FALSE)&(abs(c3.test.v.ud.gender[a,b,d])>10))
      {trimmed.v.ud.gender[a,b,d]<-NA}
    }
  }
}
```

Intercept-only models
```{r,echo=FALSE,message=FALSE,warning=FALSE}
#For columns: Do 1, 5, and 9 to get at no DIF no impact condition with N=25, N=50, and N=100, respectively
#For u indices: 1 through 4, 9 through 12 will be frat; 5 through 9, 13 through 16 will be gender
#Do we want to use u indices?

plot(-100,xlim=c(0,7.5),ylim=c(-2,2.25),xlab="",ylab="Bias",xaxt="n",main="Alcohol Consequences, no DIF in either data-generating or fitted model",cex.main=.85)
boxplot(trimmed.bch.io.frat[,1,1]-.6642,at=.25,col="white",add=TRUE)
boxplot(trimmed.bch.io.frat[,5,1]-.6642,at=.75,col="gray88",add=TRUE)
boxplot(trimmed.bch.io.frat[,9,1]-.6642,at=1.25,col="gray44",add=TRUE)
boxplot(trimmed.bch.io.frat[,1,2]-.6642,at=2.25,col="white",add=TRUE)
boxplot(trimmed.bch.io.frat[,5,2]-.6642,at=2.75,col="gray88",add=TRUE)
boxplot(trimmed.bch.io.frat[,9,2]-.6642,at=3.25,col="gray44",add=TRUE)
boxplot(trimmed.v.io.frat[,1,1]-.6642,at=4.25,col="white",add=TRUE)
boxplot(trimmed.v.io.frat[,5,1]-.6642,at=4.75,col="gray88",add=TRUE)
boxplot(trimmed.v.io.frat[,9,1]-.6642,at=5.25,col="gray44",add=TRUE)
boxplot(trimmed.v.io.frat[,1,2]-.6642,at=6.25,col="white",add=TRUE)
boxplot(trimmed.v.io.frat[,5,2]-.6642,at=6.75,col="gray88",add=TRUE)
boxplot(trimmed.v.io.frat[,9,2]-.6642,at=7.25,col="gray44",add=TRUE)
text(.75,-2,"BCH, Short",cex=.75)
text(2.75,-2,"BCH, Long",cex=.75)
text(4.75,-2,"Vermunt, Short",cex=.75)
text(6.75,-2,"Vermunt, Long",cex=.75)
abline(h=0,lwd=1.5)
abline(h=.066,lty=3)
abline(h=-.066,lty=3)
legend("top",legend=c("N=25","N=50","N=100"),fill=c("white","gray88","gray44"),horiz=TRUE,cex=.75,bty="n")
```

Unmodeled DIF
```{r,echo=FALSE,message=FALSE,warning=FALSE}
#For columns: Do 1, 5, and 9 to get at no DIF no impact condition with N=25, N=50, and N=100, respectively
#For u indices: 1 through 4, 9 through 12 will be frat; 5 through 9, 13 through 16 will be gender
#Do we want to use u indices?

plot(-100,xlim=c(0,7.5),ylim=c(-2,2.25),xlab="",ylab="Bias",xaxt="n",main="Alcohol Consequences, DIF in data-generating model but not fitted",cex.main=.85)
boxplot(trimmed.bch.io.frat[,2,1]-.6642,at=.25,col="white",add=TRUE)
boxplot(trimmed.bch.io.frat[,6,1]-.6642,at=.75,col="gray88",add=TRUE)
boxplot(trimmed.bch.io.frat[,10,1]-.6642,at=1.25,col="gray44",add=TRUE)
boxplot(trimmed.bch.io.frat[,2,2]-.6642,at=2.25,col="white",add=TRUE)
boxplot(trimmed.bch.io.frat[,6,2]-.6642,at=2.75,col="gray88",add=TRUE)
boxplot(trimmed.bch.io.frat[,10,2]-.6642,at=3.25,col="gray44",add=TRUE)
boxplot(trimmed.v.io.frat[,2,1]-.6642,at=4.25,col="white",add=TRUE)
boxplot(trimmed.v.io.frat[,6,1]-.6642,at=4.75,col="gray88",add=TRUE)
boxplot(trimmed.v.io.frat[,10,1]-.6642,at=5.25,col="gray44",add=TRUE)
boxplot(trimmed.v.io.frat[,2,2]-.6642,at=6.25,col="white",add=TRUE)
boxplot(trimmed.v.io.frat[,6,2]-.6642,at=6.75,col="gray88",add=TRUE)
boxplot(trimmed.v.io.frat[,10,2]-.6642,at=7.25,col="gray44",add=TRUE)
text(.75,-2,"BCH, Short",cex=.75)
text(2.75,-2,"BCH, Long",cex=.75)
text(4.75,-2,"Vermunt, Short",cex=.75)
text(6.75,-2,"Vermunt, Long",cex=.75)
abline(h=0,lwd=1.5)
abline(h=.066,lty=3)
abline(h=-.066,lty=3)
legend("top",legend=c("N=25","N=50","N=100"),fill=c("white","gray88","gray44"),horiz=TRUE,cex=.75,bty="n")
```


Modeled DIF
```{r,echo=FALSE,message=FALSE,warning=FALSE}
#For columns: Do 1, 5, and 9 to get at no DIF no impact condition with N=25, N=50, and N=100, respectively
#For u indices: 1 through 4, 9 through 12 will be frat; 5 through 9, 13 through 16 will be gender
#Do we want to use u indices?

plot(-100,xlim=c(0,7.5),ylim=c(-2,2.25),xlab="",ylab="Bias",xaxt="n",main="Alcohol Consequences, DIF in both data-generating and fitted models",cex.main=.85)
boxplot(trimmed.bch.ud.frat[,2,1]-.6642,at=.25,col="white",add=TRUE)
boxplot(trimmed.bch.ud.frat[,6,1]-.6642,at=.75,col="gray88",add=TRUE)
boxplot(trimmed.bch.ud.frat[,10,1]-.6642,at=1.25,col="gray44",add=TRUE)
boxplot(trimmed.bch.ud.frat[,2,2]-.6642,at=2.25,col="white",add=TRUE)
boxplot(trimmed.bch.ud.frat[,6,2]-.6642,at=2.75,col="gray88",add=TRUE)
boxplot(trimmed.bch.ud.frat[,10,2]-.6642,at=3.25,col="gray44",add=TRUE)
boxplot(trimmed.v.ud.frat[,2,1]-.6642,at=4.25,col="white",add=TRUE)
boxplot(trimmed.v.ud.frat[,6,1]-.6642,at=4.75,col="gray88",add=TRUE)
boxplot(trimmed.v.ud.frat[,10,1]-.6642,at=5.25,col="gray44",add=TRUE)
boxplot(trimmed.v.ud.frat[,2,2]-.6642,at=6.25,col="white",add=TRUE)
boxplot(trimmed.v.ud.frat[,6,2]-.6642,at=6.75,col="gray88",add=TRUE)
boxplot(trimmed.v.ud.frat[,10,2]-.6642,at=7.25,col="gray44",add=TRUE)
text(.75,-2,"BCH, Short",cex=.75)
text(2.75,-2,"BCH, Long",cex=.75)
text(4.75,-2,"Vermunt, Short",cex=.75)
text(6.75,-2,"Vermunt, Long",cex=.75)
abline(h=0,lwd=1.5)
abline(h=.066,lty=3)
abline(h=-.066,lty=3)
legend("top",legend=c("N=25","N=50","N=100"),fill=c("white","gray88","gray44"),horiz=TRUE,cex=.75,bty="n")
```


Intercept-only models
```{r,echo=FALSE,message=FALSE,warning=FALSE}
#For columns: Do 1, 5, and 9 to get at no DIF no impact condition with N=25, N=50, and N=100, respectively
#For u indices: 1 through 4, 9 through 12 will be frat; 5 through 9, 13 through 16 will be gender
#Do we want to use u indices?

plot(-100,xlim=c(0,7.5),ylim=c(-2,2.25),xlab="",ylab="Bias",xaxt="n",main="Alcohol Motives, no DIF in either data-generating or fitted model",cex.main=.85)
boxplot(trimmed.bch.io.frat[,1,3]-.6642,at=.25,col="white",add=TRUE)
boxplot(trimmed.bch.io.frat[,5,3]-.6642,at=.75,col="gray88",add=TRUE)
boxplot(trimmed.bch.io.frat[,9,3]-.6642,at=1.25,col="gray44",add=TRUE)
boxplot(trimmed.bch.io.frat[,1,4]-.6642,at=2.25,col="white",add=TRUE)
boxplot(trimmed.bch.io.frat[,5,4]-.6642,at=2.75,col="gray88",add=TRUE)
boxplot(trimmed.bch.io.frat[,9,4]-.6642,at=3.25,col="gray44",add=TRUE)
boxplot(trimmed.v.io.frat[,1,3]-.6642,at=4.25,col="white",add=TRUE)
boxplot(trimmed.v.io.frat[,5,3]-.6642,at=4.75,col="gray88",add=TRUE)
boxplot(trimmed.v.io.frat[,9,3]-.6642,at=5.25,col="gray44",add=TRUE)
boxplot(trimmed.v.io.frat[,1,4]-.6642,at=6.25,col="white",add=TRUE)
boxplot(trimmed.v.io.frat[,5,4]-.6642,at=6.75,col="gray88",add=TRUE)
boxplot(trimmed.v.io.frat[,9,4]-.6642,at=7.25,col="gray44",add=TRUE)
text(.75,-2,"BCH, Short",cex=.75)
text(2.75,-2,"BCH, Long",cex=.75)
text(4.75,-2,"Vermunt, Short",cex=.75)
text(6.75,-2,"Vermunt, Long",cex=.75)
abline(h=0,lwd=1.5)
abline(h=.066,lty=3)
abline(h=-.066,lty=3)
legend("top",legend=c("N=25","N=50","N=100"),fill=c("white","gray88","gray44"),horiz=TRUE,cex=.75,bty="n")
```

Unmodeled DIF
```{r,echo=FALSE,message=FALSE,warning=FALSE}
#For columns: Do 1, 5, and 9 to get at no DIF no impact condition with N=25, N=50, and N=100, respectively
#For u indices: 1 through 4, 9 through 12 will be frat; 5 through 9, 13 through 16 will be gender
#Do we want to use u indices?

plot(-100,xlim=c(0,7.5),ylim=c(-2,2.25),xlab="",ylab="Bias",xaxt="n",main="Alcohol Motives, DIF in data-generating model but not fitted",cex.main=.85)
boxplot(trimmed.bch.io.frat[,2,3]-.6642,at=.25,col="white",add=TRUE)
boxplot(trimmed.bch.io.frat[,6,3]-.6642,at=.75,col="gray88",add=TRUE)
boxplot(trimmed.bch.io.frat[,10,3]-.6642,at=1.25,col="gray44",add=TRUE)
boxplot(trimmed.bch.io.frat[,2,4]-.6642,at=2.25,col="white",add=TRUE)
boxplot(trimmed.bch.io.frat[,6,4]-.6642,at=2.75,col="gray88",add=TRUE)
boxplot(trimmed.bch.io.frat[,10,4]-.6642,at=3.25,col="gray44",add=TRUE)
boxplot(trimmed.v.io.frat[,2,3]-.6642,at=4.25,col="white",add=TRUE)
boxplot(trimmed.v.io.frat[,6,3]-.6642,at=4.75,col="gray88",add=TRUE)
boxplot(trimmed.v.io.frat[,10,3]-.6642,at=5.25,col="gray44",add=TRUE)
boxplot(trimmed.v.io.frat[,2,4]-.6642,at=6.25,col="white",add=TRUE)
boxplot(trimmed.v.io.frat[,6,4]-.6642,at=6.75,col="gray88",add=TRUE)
boxplot(trimmed.v.io.frat[,10,4]-.6642,at=7.25,col="gray44",add=TRUE)
text(.75,-2,"BCH, Short",cex=.75)
text(2.75,-2,"BCH, Long",cex=.75)
text(4.75,-2,"Vermunt, Short",cex=.75)
text(6.75,-2,"Vermunt, Long",cex=.75)
abline(h=0,lwd=1.5)
abline(h=.066,lty=3)
abline(h=-.066,lty=3)
legend("top",legend=c("N=25","N=50","N=100"),fill=c("white","gray88","gray44"),horiz=TRUE,cex=.75,bty="n")
```


Modeled DIF
```{r,echo=FALSE,message=FALSE,warning=FALSE}
#For columns: Do 1, 5, and 9 to get at no DIF no impact condition with N=25, N=50, and N=100, respectively
#For u indices: 1 through 4, 9 through 12 will be frat; 5 through 9, 13 through 16 will be gender
#Do we want to use u indices?

plot(-100,xlim=c(0,7.5),ylim=c(-2,2.25),xlab="",ylab="Bias",xaxt="n",main="Alcohol Motives, DIF in both data-generating and fitted models",cex.main=.85)
boxplot(trimmed.bch.ud.frat[,2,3]-.6642,at=.25,col="white",add=TRUE)
boxplot(trimmed.bch.ud.frat[,6,3]-.6642,at=.75,col="gray88",add=TRUE)
boxplot(trimmed.bch.ud.frat[,10,3]-.6642,at=1.25,col="gray44",add=TRUE)
boxplot(trimmed.bch.ud.frat[,2,4]-.6642,at=2.25,col="white",add=TRUE)
boxplot(trimmed.bch.ud.frat[,6,4]-.6642,at=2.75,col="gray88",add=TRUE)
boxplot(trimmed.bch.ud.frat[,10,4]-.6642,at=3.25,col="gray44",add=TRUE)
boxplot(trimmed.v.ud.frat[,2,3]-.6642,at=4.25,col="white",add=TRUE)
boxplot(trimmed.v.ud.frat[,6,3]-.6642,at=4.75,col="gray88",add=TRUE)
boxplot(trimmed.v.ud.frat[,10,3]-.6642,at=5.25,col="gray44",add=TRUE)
boxplot(trimmed.v.ud.frat[,2,4]-.6642,at=6.25,col="white",add=TRUE)
boxplot(trimmed.v.ud.frat[,6,4]-.6642,at=6.75,col="gray88",add=TRUE)
boxplot(trimmed.v.ud.frat[,10,4]-.6642,at=7.25,col="gray44",add=TRUE)
text(.75,-2,"BCH, Short",cex=.75)
text(2.75,-2,"BCH, Long",cex=.75)
text(4.75,-2,"Vermunt, Short",cex=.75)
text(6.75,-2,"Vermunt, Long",cex=.75)
abline(h=0,lwd=1.5)
abline(h=.066,lty=3)
abline(h=-.066,lty=3)
legend("top",legend=c("N=25","N=50","N=100"),fill=c("white","gray88","gray44"),horiz=TRUE,cex=.75,bty="n")
```